HMM Model

### 2020-10-31 manuscript/hmm.Rmd
Optimizing HMM hypotheses WIP

do_pp_checks <- FALSE
hhmm_hypothesis_res_list <- list()

@@

```{r}
compute_counterfactual_mortality_log_OR <- function(hmm_fit, numerator_serie_data, denominator_serie_data, day = 28) {
  if(nrow(numerator_serie_data) != nrow(denominator_serie_data)) {
    stop("Groups to compare must have equal number of rows")
  }

  numerator_data <- hmm_fit$data
  numerator_data$serie_data = numerator_serie_data

  numerator_state_probs <- posterior_epred_rect(hmm_fit, newdata = numerator_data, method = posterior_epred_state_prob)

  denominator_data <- hmm_fit$data
  denominator_data$serie_data = denominator_serie_data

  denominator_state_probs <- posterior_epred_rect(hmm_fit, newdata = denominator_data, method = posterior_epred_state_prob)

  mortality_state <- which(hmm_fit$data$hidden_state_data$id == "Death")
  samples_probs_numerator <- 
    rowMeans(numerator_state_probs[mortality_state, day + 1, ,])
  samples_probs_denominator <- 
    rowMeans(denominator_state_probs[mortality_state, day + 1, ,])

  log_odds_numerator <- log(samples_probs_numerator) - log1p(-samples_probs_numerator)
  log_odds_denominator <- log(samples_probs_denominator) - log1p(-samples_probs_denominator)

  log_odds_numerator - log_odds_denominator
}

evaluate_treatment_hypothesis <- function(fit, hypothesis, treatment_column, model_subgroup, adjusted, model_check) {
  counterfactual_took <- serie_data_28 %>% mutate({{ treatment_column }} := 1)
  counterfactual_no <- serie_data_28 %>% mutate({{treatment_column }} := 0)

  log_OR_samples <- compute_counterfactual_mortality_log_OR(fit, counterfactual_took, counterfactual_no, day = 28)

  bayesian_hypothesis_res_from_draws(
    draws = log_OR_samples,
    model = paste0("HMM", model_subgroup),
    estimand = "log(OR)",
    hypothesis = hypothesis,
    adjusted = adjusted,
    model_check = model_check
  )
}

evaluate_all_treatment_hypotheses <- function(fit, model_subgroup, adjusted, model_check) {
  rbind(
    evaluate_treatment_hypothesis(fit, hypotheses$hcq_reduces_death, took_hcq, model_subgroup = model_subgroup, adjusted = adjusted, model_check = model_check),
    evaluate_treatment_hypothesis(fit, hypotheses$az_reduces_death, took_az, model_subgroup = model_subgroup, adjusted = adjusted, model_check = model_check),
    evaluate_treatment_hypothesis(fit, hypotheses$favipiravir_reduces_death, took_favipiravir, model_subgroup = model_subgroup, adjusted = adjusted, model_check = model_check)
  )
}

@@

@@

```{r}
hhmm_hypothesis_res_list[["trt_group_m2"]] <- evaluate_all_treatment_hypotheses(trt_group_m2_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive, age, sex", model_check = "Suspicious")
```

@@

```{r}
hhmm_hypothesis_res_list[["trt_group_m3"]] <-  evaluate_all_treatment_hypotheses(trt_group_m3_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive, age, sex, hospital", model_check = "OK")
```

@@

```{r}
hhmm_hypothesis_res_list[["trt_group_m4"]] <-  evaluate_all_treatment_hypotheses(trt_group_m4_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive, age, sex, hospital, comorbidities", model_check = "OK")
```

@@

```{r}
hhmm_hypothesis_res_list[["trt_rate_m1"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m1_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive", model_check = "Suspicious")
```

@@

```{r}
hhmm_hypothesis_res_list[["trt_rate_m2"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m2_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex", model_check = "Suspicious")
```

@@

```{r}
hhmm_hypothesis_res_list[["trt_rate_m3"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m3_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex, hospital", model_check = "OK")
```

@@

```{r}
hhmm_hypothesis_res_list[["trt_rate_m4"]] <- evaluate_all_treatment_hypotheses(trt_rate_m4_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex, hospital, comorbidities", model_check = "OK")
```

@@

```{r}
draws <- tidybayes::tidy_draws(d_dimer_m1_fit$brmsfit)
hhmm_hypothesis_res_list[["d_dimer_m1_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_log_peak_d_dimer,
    model = "HMM",
    estimand = "log(HR)",
    hypothesis = hypotheses$d_dimer_increases_death,
    adjusted = "supportive, age, sex, hospital"
  )

@@

draws <- tidybayes::tidy_draws(trt_m7_fit$brmsfit)
hhmm_hypothesis_res_list[["trt_m7_IL_6_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_log_peak_IL_6,
    model = "HMM",
    estimand = "log(HR)",
    hypothesis = hypotheses$IL_6_increases_death,
    adjusted = "age, sex, hospital"
  )

@@

```{r}
hhmm_hypothesis_res_list[["c_trt_rate_m1"]] <- evaluate_all_treatment_hypotheses(c_trt_m1_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive", model_check = "Suspicious")
```

@@

```{r}
hhmm_hypothesis_res_list[["c_trt_rate_m2"]] <- evaluate_all_treatment_hypotheses(c_trt_m2_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex", model_check = "Suspicious")

@@

```{r}
hhmm_hypothesis_res_list[["c_trt_rate_m3"]] <- evaluate_all_treatment_hypotheses(c_trt_m3_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex, hospital", model_check = "Suspicious")

@@

```{r}
hhmm_hypothesis_res_list[["c_trt_rate_m4"]] <- evaluate_all_treatment_hypotheses(c_trt_m4_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex, hospital, comorbidities", model_check = "Suspicious")

@@

```{r}
hmm_hypothesis_res_all <- do.call(rbind, hhmm_hypothesis_res_list)
write_csv(hmm_hypothesis_res_all, path = here::here("manuscript", "hmm_res.csv"))
```

>>>>

do_pp_checks <- FALSE
hmm_hypothesis_res_list <- list()

@@

```{r}

@@

```{r}
read_csv("hmm_res.csv")
```

@@

```{r}
hmm_hypothesis_res_list[["trt_group_m2"]] <- evaluate_all_treatment_hypotheses(trt_group_m2_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive, age, sex", model_check = "Suspicious")
```

@@

```{r}
hmm_hypothesis_res_list[["trt_group_m3"]] <-  evaluate_all_treatment_hypotheses(trt_group_m3_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive, age, sex, hospital", model_check = "OK")
```

@@

```{r}
hmm_hypothesis_res_list[["trt_group_m4"]] <-  evaluate_all_treatment_hypotheses(trt_group_m4_fit, model_subgroup = "simple_group", adjusted ="all treatments, supportive, age, sex, hospital, comorbidities", model_check = "OK")
```

@@

```{r}
hmm_hypothesis_res_list[["trt_rate_m1"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m1_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive", model_check = "Suspicious")
```

@@

```{r}
hmm_hypothesis_res_list[["trt_rate_m2"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m2_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex", model_check = "Suspicious")
```

@@

```{r}
hmm_hypothesis_res_list[["trt_rate_m3"]] <-  evaluate_all_treatment_hypotheses(trt_rate_m3_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex, hospital", model_check = "OK")
```

@@

```{r}
hmm_hypothesis_res_list[["trt_rate_m4"]] <- evaluate_all_treatment_hypotheses(trt_rate_m4_fit, model_subgroup = "simple_rate", adjusted ="all treatments, supportive, age, sex, hospital, comorbidities", model_check = "OK")
```

@@

```{r}
draws <- tidybayes::tidy_draws(d_dimer_m1_fit$brmsfit)
hmm_hypothesis_res_list[["d_dimer_m1_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_log_peak_d_dimer,
    model = "HMM",
    estimand = "log(HR)",
    hypothesis = hypotheses$d_dimer_increases_death,
    adjusted = "supportive, age, sex, hospital"
  )

@@

draws <- tidybayes::tidy_draws(trt_m7_fit$brmsfit)
hmm_hypothesis_res_list[["trt_m7_IL_6_death"]] <-
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_log_peak_IL_6,
    model = "HMM",
    estimand = "log(HR)",
    hypothesis = hypotheses$IL_6_increases_death,
    adjusted = "age, sex, hospital"
  )

@@

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m1"]] <- evaluate_all_treatment_hypotheses(c_trt_m1_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive", model_check = "Suspicious")
```

@@

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m2"]] <- evaluate_all_treatment_hypotheses(c_trt_m2_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex", model_check = "Suspicious")

@@

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m3"]] <- evaluate_all_treatment_hypotheses(c_trt_m3_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex, hospital", model_check = "Suspicious")

@@

```{r}
hmm_hypothesis_res_list[["c_trt_rate_m4"]] <- evaluate_all_treatment_hypotheses(c_trt_m4_fit, model_subgroup = "complex_group", adjusted ="all treatments, supportive, age, sex, hospital, comorbidities", model_check = "Suspicious")

@@

```{r}
hmm_hypothesis_res_all <- do.call(rbind, hmm_hypothesis_res_list)
write_csv(hmm_hypothesis_res_all, path = here::here("manuscript", "hmm_res.csv"))
```
